---
title: "Schedule"
description: |
  Schedule for Math 152, Statistical Theory, Fall 2022
execute: 
  message: false
  warning: false
---

```{r}
#| echo: false
library(tidyverse)
library(kableExtra)
library(knitr)
```

Here's your roadmap for the semester! Each week, follow the general process outlined below:

-   Enjoy the notes / text <i class="fas fa-book-open"></i>

-   Attend class, review the <i class="fas fa-pencil-alt"></i>warm-up and solutions if you have any questions after completing it during class.

-   Complete the HW assignment (<i class="fa-solid fa-file-pdf"></i> pdf & <i class="fa-brands fa-r-project"></i> Rmd linked below), <i class="fa-solid fa-paper-plane"></i> submit the assignment via Gradescope accessed on the course Canvas site.

-   Discuss the reflection questions <i class="fas fa-lightbulb" target="_blank"></i> and ethics considerations <i class="fas fa-balance-scale"></i> (see the <i class="fas fa-book-open"></i> class notes) with your classmates, mentor, and professor.

-   The textbook is **Probability and Statistics** (P&S), by DeGroot and Schervish (either 3rd or 4th edition is fine).  You should be able to find it online.


```{r echo = FALSE}
schedule <- tribble(
  ~`date`, ~agenda, ~readings, ~homework, ~`handouts`, ~`warm-ups`,
  "Week 1 <br> 8.30.22", 
  '• logistics + <br>• priors + <br>• posteriors',
  'P&S: 7.1-7.2 <br> <a href="http://st47s.com/Math152/Notes/bayesian-estimation.html#bayes-rule" target = "_blank"><i class="fas fa-book-open"></i> Bayes (2.1, 2.2, 2.3)</a>', 
  '<a href="https://m152-stat-theory.netlify.app/handout/MA152_HW1f22.pdf" target = "_blank"><i class="fa-solid fa-file-pdf"></i> HW1 pdf</a> <br> <a href="https://m152-stat-theory.netlify.app/handout/MA152_HW1f22.Rmd" target = "_blank"><i class="fa-brands fa-r-project"></i> HW1 Rmd</a> <br> <a href="https://canvas.pomona.edu/" target = "_blank"><i class="fa-solid fa-paper-plane"></i> HW1 turn-in</a>',
  '<a href="handout/CB_distsheet.pdf" target = "_blank">Distribution Sheet</a>',
  '<a href="https://m152-stat-theory.netlify.app/handout/wu1_ma152_f22.pdf" target = "_blank"><i class="fas fa-pencil-alt"></i> WU 1</a> <br> <a href="https://m152-stat-theory.netlify.app/hw/wu2_ma152_f22.pdf" target = "_blank"><i class="fas fa-pencil-alt"></i> WU 2</a>',
  
"Week 2 <br> 9.6.22", 
  '• posteriors + <br> • Bayes estimators',
  'P&S: 7.3-7.4 <br> <a href="http://st47s.com/Math152/Notes/bayesian-estimation.html#conjugate-prior-distributions" target = "_blank"><i class="fas fa-book-open"></i> Bayes (2.4, 2.4, 2.6, 2.7)</a>',
  '<a href="https://m152-stat-theory.netlify.app/handout/MA152_HW2f22.pdf" target = "_blank"><i class="fa-solid fa-file-pdf"></i> HW2 pdf</a> <br> <a href="https://m152-stat-theory.netlify.app/handout/MA152_HW2f22.Rmd" target = "_blank"><i class="fa-brands fa-r-project"></i> HW2 Rmd</a> <br> <a href="https://canvas.pomona.edu/" target = "_blank"><i class="fa-solid fa-paper-plane"></i> HW2 turn-in</a>',
  '<a href="handout/baseball_bayes_2022.pdf" target = "_blank">Baseball and Bayes</a>',
  '<a href="https://m152-stat-theory.netlify.app/handout/wu3_ma152_f22.pdf" target = "_blank"><i class="fas fa-pencil-alt"></i> WU 3</a> <br> <a href="https://m152-stat-theory.netlify.app/handout/wu4_ma152_f22.pdf" target = "_blank"><i class="fas fa-pencil-alt"></i> WU 4</a>',

"Week 3 <br> 9.13.22",   
  '• MLE + <br> • consistency + <br> • bias + <br> • MOM',
  'P&S: 7.5-7.6 <br> <a href="https://st47s.com/Math152/Notes/intro.html" target = "_blank"><i class="fas fa-book-open"></i></a>',
  '',
  '',  
  '',
  
"Week 4 <br> 9.20.22", 
  '• sampling distributions <br>of estimators',
  'P&S: 6.1-6.3, 8.1-8.4 <br> <a href="https://st47s.com/Math152/Notes/intro.html" target = "_blank"><i class="fas fa-book-open"></i></a>',
  '',
  '',
  '',
  
  
"Week 5 <br> 9.27.22",
  '• bootstrap sampling <br>distributions',
  'P&S: 12.6 <br> <a href="https://st47s.com/Math152/Notes/intro.html" target = "_blank"><i class="fas fa-book-open"></i></a>',
  '',
  '',
  '',
  
"Week 6 <br> 2.22.22", 
  '• frequentist, Bayesian <br>intervals',
  'P&S: 8.5-8.6 <br> <a href="https://st47s.com/Math152/Notes/intro.html" target = "_blank"><i class="fas fa-book-open"></i></a>',
  '',
  '',
  '',    

'<font color = "#114B5F"><b>Week 7 <br> 10.11.22</b></font>', 
'<font color = "#114B5F"><b>review & catch-up</b></font>',
'<font color = "#114B5F"><b>exam 1 in class<br> 10.13.22</b></font>',
  '',
  '',
  '',

'<font color = "#114B5F"><b>Tuesday <br>10.18.22</b></font>', '<font color = "#114B5F"><b>Fall Break</b></font>',"", 
  '',
  '',
  '',      

"Week 8 <br> 10.20.22", 
  '• bootstrap confidence <br>intervals <br> <br> • earthquake!',
  '<a href="https://st47s.com/Math152/Notes/intro.html" target = "_blank"><i class="fas fa-book-open"></i></a>',
  '',
  '',
  '',
  
"Week 9 <br> 10.25.22", 
  '• Fisher information + <br>• efficiency + <br>• UMVUE',
  'P&S: 8.7-8.8 <br> <a href="https://st47s.com/Math152/Notes/intro.html" target = "_blank"><i class="fas fa-book-open"></i></a>',
  '',
  '',
  '',

"Week 10 <br> 11.1.22", 
  '• hypotehsis testing + <br>• simple hypotheses',
  'P&S: 9.1 <br> <a href="https://st47s.com/Math152/Notes/intro.html" target = "_blank"><i class="fas fa-book-open"></i></a>',
  '',
  '',
  '',
  
"Week 11 <br> 11.8.22", 
  '• Neyman-Pearson',
  'P&S: 9.2 <br> <a href="https://st47s.com/Math152/Notes/intro.html" target = "_blank"><i class="fas fa-book-open"></i></a>',
  '',
  '',
  '',  

'<font color = "#114B5F"><b>Week 12 <br> 11.15.22</b></font>', 
'<font color = "#114B5F"><b>review & catch-up</b></font>',
'<font color = "#114B5F"><b>exam 2 in class<br> 10.17.22</b></font>',
  '',
  '',
  '',

"Week 13 <br> 11.22.22", 
  '• UMP',
  'P&S: 9.3 <br> <a href="https://st47s.com/Math152/Notes/intro.html" target = 
"_blank"><i class="fas fa-book-open"></i></a>',
  '',
  '',
  '',  

'<font color = "#114B5F"><b>Thursday <br>11.24.22</b></font>', '<font color = "#114B5F"><b>Thanksgiving</b></font>',"", 
  '',
  '',
  '',      

"Week 14 <br> 11.29.22", 
  '• two-sided + <br>• t-tests + <br>•  LRT + <br> goodness of fit',
  'P&S: 9.4-9.6, 10.1 <br> <a href="https://st47s.com/Math152/Notes/intro.html" target = 
"_blank"><i class="fas fa-book-open"></i></a>',
  '',
  '',
  '',

"Week 15 <br> 12.6.22", 
  '• Bayes tests + <br>• foundational ideas',
  'P&S: 9.8-9.9 <br> <a href="https://st47s.com/Math152/Notes/intro.html" target = 
"_blank"><i class="fas fa-book-open"></i></a>',
  '',
  '',
  '',  
  
"Week 14 <br> 4.26.22", 
  '',
  '',
  '',
  '',
  '',
  
'<font color = "#114B5F"><b>Thursday <br> 12.15.22 <br> 2-5pm</b></font>', '<font color = "#114B5F"><b>Final Exam </b></font>',"", 
  '',
  '',
  ''   
  )
```


```{r}
#| echo: false
#| column: body-outset
# can use column: page for the entire page
schedule %>% 
  mutate_all(linebreak) %>% # required for linebreaks to work
  kbl(escape = FALSE, align = c(rep('l',7))) %>%
  kable_styling(bootstrap_options = c("striped", "hover"),
                full_width = TRUE) %>%
  column_spec(1:6,extra_css = "vertical-align:top;")
```




